Fast and Error-Adaptive Influence Maximization based on Count-Distinct Sketches

### 2022-11-08 paper.tex
Update on Overleaf.

\maketitle
\begin{abstract}
%     \fixme{
% Influence maximization~(IM) is the problem of finding a seed vertex set that maximizes the expected number of vertices influenced under a given diffusion model. Due to the NP-Hardness of finding an optimal seed set, approximation algorithms are frequently used for IM. }
% In addition to these high-quality yet expensive approximation algorithms, lightweight, sketch-based approaches which do not step-by-step simulate the diffusion process have been proposed in the literature to cope with the scale of today's networks. 
In this work, we describe a fast, error-adaptive approach that leverages Count-Distinct sketches and hash-based fused sampling to estimate the number of influenced vertices throughout a diffusion. We use per-vertex Flajolet-Martin sketches where each sketch corresponds to a sampled subgraph. To efficiently simulate the diffusions, the reach-set cardinalities of a single vertex are stored in memory in a consecutive fashion. This allows the proposed algorithm to estimate the number of influenced vertices in a single step for simulations at once. %In addition, thanks to their efficiency, and the scalability of our parallel implementation, we can rebuild the sketches whenever it is necessary. 
For a faster IM kernel, we rebuild the sketches in parallel only after observing estimation errors above a given threshold. Our experimental results show that the proposed algorithm yields comparable seed sets while being up to $3,337\times$ faster than a state-of-the-art, high-quality influence maximization algorithm. In addition, it is up to $63\times$ faster than a sketch-based approach while producing seed sets with $2\%$--$10\%$ better influence scores.
\end{abstract}
% } 
% \begin{keyword}
% Influence Maximization, Graph Processing, Graph Sampling, Fused Sampling, Memory Access Regularization, Count-Distinct Sketch
% \end{keyword}
% \end{frontmatter}

@@

\item We evaluate the runtime performance, memory consumption, and influence score of sketch- and approximation-based state-of-the-art influence maximization algorithms, namely {\sc Skim}~\cite{cohen2014sketch}, {\sc SSA}~\cite{nguyen2016stop}, {\sc Tim+}~\cite{tim} and {\sc Imm}~\cite{minutoli2019fast}, to accurately position the performance of \acro{} within the IM literature. The experiments show that \acro can be $63\times$ and $3337\times$ faster than a state-of-the-art sketch-based and high-quality approximation algorithm, respectively while reaching the influence quality of the accurate algorithms with less memory.

@@

% \setlength{\columnsep}{1.2pt}%
\begin{wrapfigure}{r}{0.3\linewidth}
    \begin{center}
      \includegraphics[width=1\linewidth]{images/ic.pdf}
    \end{center}
    \caption{\label{fig:ic}The directed graph $G = (V, E)$ for IC with independent diffusion probabilities.}
  \end{wrapfigure}
  The {\bf Independent Cascade} model \fixme{works in rounds and activates} a vertex $v$ in the current round if one of $v$'s \fixme{incoming edges $(u, v)$ is used during the diffusion} round, \fixme{which happens with the activation probability $w_{u, v}$, given that $u$ has already been} influenced \fixme{in the previous rounds. The activation probabilities are independent (from each other and previous activations)} in the {\em independent cascade} model, which we focus on in this paper. A toy graph with activation probabilities on the edges is shown in Figure~\ref{fig:ic}.
  % In theory, there can exist parallel and independent $\{u, v\}$ edges in $E$. In practice, they are merged to a single $\{u,v\}$ edge via preprocessing. 
%As a generalization of the above-mentioned models, {\bf triggering} has also been proposed by Kempe~et~al.~\cite{kempe2003maximizing}. In this model, each neighbor has a probability to influence the vertex $v$. The diffusion process chooses a random subset of vertices called the {\em triggering set} to activate the vertices at each instance.
The complexity analysis stays consistent for many diffusion models, including {\em Independent Cascade}, {\em Weighted Cascade}, and {\em Linear Threshold} models; the time complexity of the greedy algorithm, estimating the $\sigma$ influence score, running $R$ simulations, and selecting $K$ seed vertices is $\mathcal{O}(KRn\sigma)$ for a graph with $n$ vertices. 
We concentrate on the IC model in this paper, but although their adaptation requires some work, the proposed methods are also relevant to other models in the literature.

@@

The {\em distinct element count} problem focuses on finding the number of distinct elements in a stream where the elements are coming from a universal set ${\cal U}$. Finding the number of vertices to be influenced of a candidate seed vertex $u$, i.e., the cardinality of $u$'s {\em reachability set}, is a similar problem. For each sample subgraph, the number of visited vertices is found while traversing the subgraphs starting from $u$. Note that an exact, linear-time computation of stream cardinality requires memory proportional to the universal set cardinality, i.e., ${\Theta}(|{\cal U}|)$.

@@

For directed graphs, storing reachability sets for all vertices and merging these sets are infeasible for nontrivial graphs. 
If one-hot vectors are used to store the reachability sets for constant insertion time, $\Theta(n^2\mathcal{R})$ bits of memory is required where each merge operation has $\Theta(n)$ time complexity. 
If disjoints sets are used for storing reachability sets; $\mathcal{O}(n{\sigma}\mathcal{R})$ 
%\kktodo{Gokhan bunu aciklayalim, bir de $\bar{\sigma}$ nedir}\ggx{estimated influence} 
memory is required to store all reachability sets, and each merge operation has $\mathcal{O}({\tt Ack}(\sigma))$ complexity where ${\tt Ack}$ is the Ackermann~\cite{ackermann} function. %\kktodo{bu Ackermann'a atif verelim}.\ggx{done.}

Count-Distinct~Sketches can be leveraged to estimate a reachability set's cardinality efficiently; for instance, the Flajolet–Martin~(FM) sketch~\cite{flajolet1985probabilistic} uses a constant number, ${\cal J}$, of registers where ${\cal J}$ can be increased for better estimates. Furthermore, the union of two sketches can be computed in constant time which is a necessary property for an efficient estimation of reachability set cardinalities. The essence of an FM sketch is that it keeps the track of how rare the elements are in a stream. The rarity of the stream is estimated by counting the maximum number of leading zeros in the stream elements' hash values. Initially, each register is initialized with zero. The items are hashed one by one, and the length of the longest all-zero prefix is stored in the register. With a single register, the cardinality estimation can be done by computing the power $2^r$ where $r$ is the value in the register.

@@

HyperFuser uses \emph{directed} fused sampling, utilizes \emph{sketches} for both influence estimation and seed selection, and a novel error-adaptive sketch rebuilding strategy. On the other hand, {\sc InFuseR}~\cite{infuser} employs {\emph {undirected}} hash-based fused sampling and CELF optimizations for seed selection.

@@

Throughout the process, each register is used only for a single sample/simulation. 
For an edge ($u, v$) in simulation $j$ where $v$ is a live vertex, an update, i.e., a merge operation, on $u$'s register is performed on the corresponding register $M_u$[$j$], i.e., $M_u[j] = max(M_u[j],M_v[j])$. 
The toy example in Fig.~\ref{fig:fmops} shows how the sketch operations are done on a toy problem. In Fig.~\ref{fig:fmops}(a), the sketches, in a toy problem with 4 samples and 4-bit hash functions, are initialized; the id of vertex $u$ is hashed and leading zeros of the hash are written to registers. In Fig.~\ref{fig:fmops}(a), the merge operation is illustrated on registers of vertex $u$, $M_u$, and vertex $v$, $M_v$; merge operation takes element-wise maximum of registers to find union of the reachability sets. Fig.~\ref{fig:fmops} shows writing the merged reachability sets back to registers w.r.t sampling using a conditional move operation.

\begin{figure}[!ht]
    \begin{center}
    \includegraphics[width=\linewidth]{images/fmops.pdf}
    \caption{ (a) \label{fminit} Toy sketch initialization of vertex $x$ with four registers and 4-bit hash functions. (b) \label{fmmerge} Example of union operation on sketches of vertices $x$ and $y$ with four registers. (c) \label{fmwrite} Diffusion operation from vertex $v$ to vertex $u$ w.r.t sampling in $\hat{G}$. 
     }\label{fig:fmops} 
    \end{center}
\end{figure}

That is, at each iteration, vertices (outgoing) neighbors' reachability sets are added to their sketches.
This recursive formulation of the influence iteratively relays the reachability information among the vertices, allowing us to estimate the marginal influence for all vertices very fast.
%At each iteration, the sketches of the existing reachable vertices are modified. \kktodo{onceki cumleyi de degistirdim - dogru mu} \ggx{her vertex başkasına reachable olabilir, son cumleyi çıkartabilirz}
%Instead of simulating the diffusion sample-by-sample, vertex-by-vertex, or path-by-path, all the influence that passes through the edges in a single step is processed together.

@@

After estimating the reachability set cardinalities, \acro picks the vertex $v$ with the largest cardinality by evaluating the sketches. Then it finds the (actual) reachability set of the latent seed set, which is the union of the reachability sets of $v$ and the vertices in the seed set, by performing Monte-Carlo simulations. The vertices in this reachability set are removed from the live set $L$. %labeled as {\em visited}. 
%\kktodo{niye blocked, influenced desek?}\ggx{literaturde kullanilan terim o sekilde, ben visited'i tercih ederdim, algorithmaya gore live set L den çıkartıyoruz diye güncelledim.} 
Hence, in later iterations, these vertices will not contribute to the marginal gain. Finally, the algorithm checks if rebuilding is necessary for the sketches based on the difference between the sketch estimate and Monte-Carlo estimate. The proposed approach and the algorithm will be described in this section in more detail starting with fused sampling.%\kktodo{yukaridaki cumlelerde bunlara isim verelim, burada soyleyelim matematiksel olarak - zaten isimleri var sanirim}.\ggx{malesef sembolleri,isimleri yok. $u \notin R_S$ şeklinde.}

@@

% For a given graph $G = (V,E)$, the bias of a sampling probability $x$ is computed as $|(31/2) − E(|H(m)|) / E(|H(m)|))|$ for all $(u,v) \in E$ and $0 \leq r < R$. 
% Figure~\ref{fig:prob-bias} shows the bias for 12 real-life networks. 
%Traditional implementations sample each edge in $G$ once per simulation and store them to construct a sampled subgraph. n
%Being able to generate the samples on the fly allows us to avoid many memory accesses. 
% One of the downsides of hash-based fused sampling is that we have to generate all these random values,  $P(u,v)_r$, for each edge traversal and each simulation $r$. As mentioned above, the edges' hash values are precomputed for all the edges in $E$ to reduce computation cost and leverage fused sampling's performance gains. %Fortunately, the rest of the operations, i.e., one XOR and one division, are very fast on modern computing hardware. %The trade-off between extra memory and computation here maybe not be applicable for different computation architectures and faster/simpler hash functions.

\subsection{Estimating Reachability Set Cardinality}
A greedy solution to IM requires finding a vertex with a maximum marginal influence at each step until the seed set size reaches $K$.
An exact computation of marginal influences, i.e., the additional influence when a vertex $v$ is added to the seed set, requires the computation of all candidate vertices' reachability sets within all the samples. This involves many graph traversals and is expensive even with various algorithmic optimizations and a scalable parallelized implementation, e.g., see~\cite{infuser}. %The influence estimation problem is quite similar to the Count-Distinct problem applied to all sample subgraphs, as explained above. Hence, 
In this work, we pursue the idea of using Count-Distinct sketches to estimate marginal influence scores. Here we propose an efficient and effective IM algorithm, \acro, that utilizes Flajolet–Martin sketches described in Section~\ref{sec:sketch} to estimate the averages of distinct elements in the sampled subgraphs. Algorithm~\ref{algo:main} shows the steps taken by \acro.

@@

The traditional Greedy algorithm~\cite{kempe2003maximizing} processes the simulations one-by-one and computes the vertices' reachability sets. On the other hand, \acro efficiently performs multiple simulations at once in a single-step iteration (which processes distance-1 neighborhoods). Since each iteration relays one level of cardinality information, this step requires at most $d$ iterations where $d$ is the diameter of $G$. Note that when processed individually (as the Greedy algorithm), the $j$th simulation over the sampled subgraph $G_j$ would require only at most $d_j$ iterations, which is the diameter of $G_j$, and probably much smaller than $d$ considering the sampled subgraphs being highly sparse. However, $d$ is also a loose upper bound for \acro. A better one is {\tt max}$\{d_j: 1 \leq j \leq {\cal J}\} + 1$ where $d_j$ is the diameter of $G_j$. We have observed that during these simulations later iterations have only a minor impact on the marginal influence scores. Hence, to further reduce the overhead of concurrent simulation processing and avoid bottleneck simulations due to remaining perimeter structures (e.g., paths on the perimeter), we employ an early-exit threshold $\epsilon_c$ over the remaining live vertices ratio, which is expected to be very small when only one or two (bottleneck) simulations remain. That is if $|L'| \leq |V| \times \epsilon_c$ the diffusion process in Algorithm~\ref{algo:diffusion-step} stops. Otherwise, $L$ is set to $L'$, $L'$ is cleared, and the next iteration starts. We used $\epsilon_c = 0.02$ to make \acro faster while keeping its quality almost the same. Figure~\ref{fig:hyperdiff} shows a toy problem diffusion process on 4 vertices and a single sample, the process initializes sketches using respective hashes' leading zeros and bigger numbers are pulled from all recently changed neighbors. Whereas Infuser works vertices one by one, labeling visited vertices for the processed vertex. The process is repeated for multiple vertices until a seed vertex is found. Figure~\ref{fig:infuserdiff} shows an example in the same settings as Figure~\ref{fig:hyperdiff} to emphasize the difference between the two algorithms.

@@

\hline
\multirow{6}{*}{\scriptsize\rotatebox[origin=c]{90}{Directed}}&{\tt Epinions} & 75,880 & 508,838  & 6.71 & 14\\
&{\tt Friendster} & 65,608,366 & 1,806,067,135  & 27.53 & 32\\
&{\tt LiveJournal} & 4,847,571 & 68,993,773  & 14.23 & 16\\
&{\tt Pokec} & 1,632,803 & 30,622,564  & 18.75 & 11\\
&{\tt Slashdot0811} & 77,360 & 905,468  & 11.70 & 10\\
&{\tt Slashdot0902} & 82,168 & 948,464  & 11.54 & 11\\
% &{\tt Twitter} & 81,306 & 2,420,766 & 1.37 & 29.77 
\end{tabular}
}
\end{table}
% \FloatBarrier
\subsection{Experiment Settings} \label{sec:expset}

@@

We evaluated our method against three other state-of-the-art influence maximization algorithms, {\sc Tim+}, {\sc Skim}, {\sc Imm}, and {\sc Ssa}. The first algorithm focuses on the influence score, whereas the second is a sketch-based algorithm that takes the execution time into account. The third one is a scalable, parallel approximation algorithm with a parameter to control the influence quality, and the last one leverages a Stop-and-Stare strategy.

@@

\item Minutoli et al.'s {\sc Imm} is a high-performance, parallel algorithm that efficiently produces accurate seed sets~\cite{minutoli2019fast}. 
It is an approximation method that improves the Reverse Influence Sampling~(RIS)~\cite{borgs2014maximizing} algorithm by eliminating the need for the threshold to be used. %{\sc Imm} generalizes the influence of all vertices on a small set of sample graphs that is sampled from the reachability sets of a few vertices. 
We have used $\epsilon = 0.5$ as suggested in the original paper, where $\epsilon$ is a user-defined parameter to control the approximation boundaries.

@@

\subsection{Comparing \acro with State-of-the-Art}
To compare the run time, memory use, and quality of \acro with those of the state-of-the-art, %As explained above, the parameters of the experimented methods are hard to compare directly. It is infeasible to find precisely the corresponding parameter between any two methods in this setting. For that reason, we have used the parameters suggested by the paper.
we perform experiments using the following parameters controlling the quality of the seed sets: {\sc Tim+} ($\epsilon=0.2$), {\sc Imm} ($\epsilon=0.5$), {\sc Skim} ($l=64,k=64$), and {\sc Ssa}($\epsilon=0.1$). 
In fact, one of the drawbacks of \acro is that it does not have a direct control over the approximation factor, whereas {\sc Tim+} and {\sc Imm} have one. Still, \acro can control the quality indirectly by tuning the number of Monte-Carlo simulations ${\cal J}$ which also increases the number of sketches used per vertex. In the experiments, we have used ${\cal J} = 256$ for \acro. In addition, as explained in the previous section, we use a global error threshold $\epsilon_{g} = 0.01$, a local error threshold as $\epsilon_l=0.3$, and the early-exit ratio as $\epsilon_{c}=0.02$.\looseness=-1

>>>>

\maketitle
\begin{abstract}
%     \fixme{
Influence maximization~(IM) is the problem of finding a seed vertex set that maximizes the expected number of vertices influenced under a given diffusion model. Due to the NP-Hardness of finding an optimal seed set, approximation algorithms are frequently used for IM. 
% }
In addition to these high-quality yet expensive approximation algorithms, lightweight, sketch-based approaches, which do not step-by-step simulate the diffusion process, have been proposed in the literature to cope with the scale of today's networks. 
In this work, we describe a fast, error-adaptive approach that leverages Count-Distinct sketches and hash-based fused sampling to estimate, not to count, the number of influenced vertices throughout a diffusion. We use per-vertex Flajolet-Martin sketches where each sketch corresponds to a sampled subgraph. To efficiently simulate the diffusions, the reach-set cardinalities of a single vertex are stored in memory in a consecutive fashion. This allows the proposed algorithm to estimate the number of influenced vertices in a single step for simulations at once. %In addition, thanks to their efficiency, and the scalability of our parallel implementation, we can rebuild the sketches whenever it is necessary. 
For a faster IM kernel, we rebuild the sketches in parallel only after observing estimation errors above a given threshold. Our experimental results show that the proposed algorithm yields comparable seed sets while being up to $3,337\times$ faster than a state-of-the-art, high-quality influence maximization algorithm. In addition, it is up to $63\times$ faster than a sketch-based approach while producing seed sets with $2\%$--$10\%$ better influence scores.
\end{abstract}
% } 
% \begin{keyword}
% Influence Maximization, Graph Processing, Graph Sampling, Fused Sampling, Memory Access Regularization, Count-Distinct Sketch
% \end{keyword}
% \end{frontmatter}

@@

\item We evaluate the runtime performance, memory consumption, and influence score of sketch- and approximation-based state-of-the-art influence maximization algorithms, namely {\sc Skim}~\cite{cohen2014sketch}, {\sc SSA}~\cite{nguyen2016stop}, {\sc Tim+}~\cite{tim} and {\sc Ripples}~\cite{minutoli2019fast}, to accurately position the performance of \acro{} within the IM literature. The experiments show that \acro can be $63\times$ and $3337\times$ faster than a state-of-the-art sketch-based and high-quality approximation algorithm, respectively while reaching the influence quality of the accurate algorithms with less memory.

@@

% \setlength{\columnsep}{1.2pt}%
\begin{wrapfigure}{r}{0.35\linewidth}
    \begin{center}
      \includegraphics[width=1\linewidth]{images/ic.pdf}
    \end{center}
    \caption{\label{fig:ic}The directed graph $G = (V, E)$ for IC with independent diffusion probabilities.}
  \end{wrapfigure}
  The {\bf Independent Cascade} model \fixme{works in rounds and activates} a vertex $v$ in the current round if one of $v$'s \fixme{incoming edges $(u, v)$ is used during the diffusion} round, \fixme{which happens with the activation probability $w_{u, v}$, given that $u$ has already been} influenced \fixme{in the previous rounds. The activation probabilities are independent (from each other and previous activations)} in the {\em independent cascade} model, which we focus on in this paper. A toy graph with activation probabilities on the edges is shown in Figure~\ref{fig:ic}.
  % In theory, there can exist parallel and independent $\{u, v\}$ edges in $E$. In practice, they are merged to a single $\{u,v\}$ edge via preprocessing. 
%As a generalization of the above-mentioned models, {\bf triggering} has also been proposed by Kempe~et~al.~\cite{kempe2003maximizing}. In this model, each neighbor has a probability to influence the vertex $v$. The diffusion process chooses a random subset of vertices called the {\em triggering set} to activate the vertices at each instance.
The complexity analysis stays consistent for many diffusion models, including {\em Independent Cascade}, {\em Weighted Cascade}, and {\em Linear Threshold} models; the time complexity of the greedy algorithm, estimating the $\sigma$ influence score, running $R$ simulations, and selecting $K$ seed vertices is $\mathcal{O}(KRn\sigma)$ for a graph with $n$ vertices. 
We concentrate on the IC model in this paper, but although their adaptation requires some work, the proposed methods are also relevant to other models in the literature.

@@

The {\em distinct element count} problem focuses on finding the number of distinct elements in a stream where the elements are coming from a universal set ${\cal U}$. Finding the number of vertices to be influenced of a candidate seed vertex $u$, i.e., the cardinality of $u$'s {\em reachability set}, is a similar problem. For each sample subgraph, the number of visited vertices is found while traversing the subgraphs starting from $u$. Note that an exact, linear-time computation of stream cardinality requires memory proportional to the universal set cardinality, i.e., ${\Theta}(|{\cal U}|)$. Via sketches, \acro can estimate the reachability set cardinalities with much less memory and computation compared to the exact counting solutions.

@@

For directed graphs, storing reachability sets for all vertices and merging these sets are infeasible for nontrivial graphs. 
If one-hot vectors are used to store the reachability sets for constant insertion time, $\Theta(n^2\mathcal{R})$ bits of memory are required where each merge operation has $\Theta(n)$ time complexity. 
If disjoints sets are used for storing reachability sets; $\mathcal{O}(n{\sigma}\mathcal{R})$ 
%\kktodo{Gokhan bunu aciklayalim, bir de $\bar{\sigma}$ nedir}\ggx{estimated influence} 
memory is required to store all reachability sets, and each merge operation has $\mathcal{O}({\tt Ack}(\sigma))$ complexity where ${\tt Ack}$ is the Ackermann~\cite{ackermann} function. %\kktodo{bu Ackermann'a atif verelim}.\ggx{done.}

Count-Distinct~Sketches can be leveraged to estimate a reachability set's cardinality efficiently; for instance, the Flajolet–Martin~(FM) sketch~\cite{flajolet1985probabilistic} uses a constant number, ${\cal J}$, of registers where ${\cal J}$ can be increased for better estimates. Furthermore, the union of two sketches can be computed in constant time which is a necessary property for an efficient estimation of reachability set cardinalities. The essence of an FM sketch is that it keeps track of how rare the elements are in a stream. The rarity of the stream is estimated by counting the maximum number of leading zeros in the stream elements' hash values. Initially, each register is initialized with zero. The items are hashed one by one, and the length of the longest all-zero prefix is stored in the register. With a single register, the cardinality estimation can be done by computing the power $2^r$ where $r$ is the value in the register.

@@

\acro{} uses {\em directed} fused sampling, utilizes \emph{sketches} for both influence estimation and seed selection, and a novel error-adaptive sketch rebuilding strategy. An IM tool leveraging fusing is~{\sc InFuseR}~\cite{infuser} which employs {\emph {undirected}} hash-based fused sampling and CELF optimizations~\cite{CELF} for seed selection to find the best seed set. Unlike {\sc InFuseR}, \acro{} follows a completely different approach and only estimates the cardinalities of the reachability sets and do not compute them.

@@

%At each iteration, the sketches of the existing reachable vertices are modified. \kktodo{onceki cumleyi de degistirdim - dogru mu} \ggx{her vertex başkasına reachable olabilir, son cumleyi çıkartabilirz}
%Instead of simulating the diffusion sample-by-sample, vertex-by-vertex, or path-by-path, all the influence that passes through the edges in a single step is processed together.

@@

\acro performs $K$ iterations to find $K$ vertices. Each iteration starts by estimating the reachability set cardinalities for all the vertices and keeping this information within sketches. After this, \acro picks the vertex $v$ with the largest cardinality by evaluating these sketches. It then finds the (actual) reachability set of the latent seed set, which is the union of the reachability sets of $v$ and the vertices in the seed set, by performing Monte-Carlo simulations. The vertices in this reachability set are removed from the live set $L$. %labeled as {\em visited}. 
%\kktodo{niye blocked, influenced desek?}\ggx{literaturde kullanilan terim o sekilde, ben visited'i tercih ederdim, algorithmaya gore live set L den çıkartıyoruz diye güncelledim.} 
Hence, in later iterations, these vertices will not contribute to the marginal gain. Although the same sketch memory can be used for a couple of iterations, i.e., seed vertex searches, we have observed that sketches become dirty and a rebuild is necessary. Hence, finally, the algorithm checks if sketch rebuilding is necessary based on the difference between the sketch estimate and Monte-Carlo estimate. The proposed approach and the algorithm is described here in more detail starting with fused sampling.%\kktodo{yukaridaki cumlelerde bunlara isim verelim, burada soyleyelim matematiksel olarak - zaten isimleri var sanirim}.\ggx{malesef sembolleri,isimleri yok. $u \notin R_S$ şeklinde.}

@@

% For a given graph $G = (V,E)$, the bias of a sampling probability $x$ is computed as $|(31/2) − E(|H(m)|) / E(|H(m)|))|$ for all $(u,v) \in E$ and $0 \leq r < R$. 
% Figure~\ref{fig:prob-bias} shows the bias for 12 real-life networks. 
%Traditional implementations sample each edge in $G$ once per simulation and store them to construct a sampled subgraph. n
%Being able to generate the samples on the fly allows us to avoid many memory accesses. 
% One of the downsides of hash-based fused sampling is that we have to generate all these random values,  $P(u,v)_r$, for each edge traversal and each simulation $r$. As mentioned above, the edges' hash values are precomputed for all the edges in $E$ to reduce computation cost and leverage fused sampling's performance gains. %Fortunately, the rest of the operations, i.e., one XOR and one division, are very fast on modern computing hardware. %The trade-off between extra memory and computation here maybe not be applicable for different computation architectures and faster/simpler hash functions.
\subsection{Estimating Reachability Set Cardinalities}

To estimate the cardinality of a reachability set, \acro{} performs a cheap diffusion process over the sample subgraphs by using a single sketch register for a single sample/simulation. 
For an edge ($u, v$) in simulation $j$ where $v$ is a live vertex, an update, i.e., a merge operation, on $u$'s register is performed on the corresponding register $M_u$[$j$], i.e., $M_u[j] = max(M_u[j],M_v[j])$. 
The toy example in Fig.~\ref{fig:fmops} with  ${\cal J} = 4$ shows how the sketch operations are done on a toy problem. In Fig.~\ref{fig:fmops}(a), the sketches, in a toy problem with 4 samples and 4-bit hash functions, are initialized; the id of vertex $u$ is hashed and leading zeros of the hash are written to registers. In Fig.~\ref{fig:fmops}(b), the merge operation is illustrated on registers of vertex $u$, $M_u$, and vertex $v$, $M_v$; merge operation takes element-wise maximum of registers to find union of the reachability sets. All these operations are performed using vectorized instructions.

 To vectorize the rest of the process, we leverage conditional move operations. Although an edge ($u, v$) is inside the graph, it may not be in all the samples. In the toy example of Fig.~\ref{fig:fmops}, we assume that ($u, v$) only exists in the first and the last sample. 
 Fig.~\ref{fig:fmops}(c) writes the merged reachability sets back to $u$'s registers. For the first sample, $M_u[1]$ needs an update. The operations for the second and the third rows/samples are skipped since ($u, v$) does not exist in these samples. The fourth row shows the case with ($u$, $v$) is in the sample but $M_u[4] < M_v[4]$. Hence, the move operation is not needed. However, for such cases, we still perform this write as a part of the vectorized operation. This being said, we skip the whole Fig.~\ref{fig:fmops}(c) when ($u, v$) is not in any of these samples.

\begin{figure}[!ht]
    \begin{center}
    \includegraphics[width=\linewidth]{images/fmops.pdf}
    \caption{ (a) \label{fminit} Toy sketch initialization of vertex $u$ with four registers and 4-bit hash functions. (b) \label{fmmerge} Example of union operation on sketches of vertices $u$ and $v$ with four registers. (c) \label{fmwrite} Diffusion operation from vertex $v$ to vertex $u$ w.r.t. sampled subgraph. 
     }\label{fig:fmops} 
    \end{center}
\end{figure}

To summarize, at each iteration, vertices (outgoing) neighbors' reachability sets are added to their sketches.
This recursive formulation of the influence iteratively relays the reachability information among the vertices, allowing us to estimate the marginal influence for all vertices very fast.

\subsection{Finding the Seed Set}
A greedy solution to IM requires finding a vertex with a maximum marginal influence at each step until the seed set size reaches $K$.
An exact computation of marginal influences, i.e., the additional influence when a vertex $v$ is added to the seed set, requires the computation of all candidate vertices' reachability sets within all the samples. This involves many graph traversals and is expensive even with various algorithmic optimizations and a scalable parallelized implementation, e.g., see~\cite{infuser}. %The influence estimation problem is quite similar to the Count-Distinct problem applied to all sample subgraphs, as explained above. Hence, 
In this work, we pursue the idea of using Count-Distinct sketches to estimate marginal influence scores. Here we propose an efficient and effective IM algorithm, \acro, that utilizes Flajolet–Martin sketches described in Section~\ref{sec:sketch} to estimate the averages of distinct elements in the sampled subgraphs. Algorithm~\ref{algo:main} shows the steps taken by \acro.

@@

The traditional Greedy algorithm~\cite{kempe2003maximizing} processes the simulations one-by-one and computes the vertices' reachability sets. On the other hand, \acro efficiently performs multiple simulations at once in a single-step iteration (which processes distance-1 neighborhoods). Since each iteration relays one level of cardinality information, this step requires at most $d$ iterations where $d$ is the diameter of $G$. Note that when processed individually (as the Greedy algorithm), the $j$th simulation over the sampled subgraph $G_j$ would require only at most $d_j$ iterations, which is the diameter of $G_j$, and probably much smaller than $d$ considering the sampled subgraphs being highly sparse. However, $d$ is also a loose upper bound for \acro. A better one is {\tt max}$\{d_j: 1 \leq j \leq {\cal J}\} + 1$ where $d_j$ is the diameter of $G_j$. We have observed that during these simulations later iterations have only a minor impact on the marginal influence scores. Hence, to further reduce the overhead of concurrent simulation processing and avoid bottleneck simulations due to remaining perimeter structures (e.g., paths on the perimeter), we employ an early-exit threshold $\epsilon_c$ over the remaining live vertices ratio, which is expected to be very small when only one or two (bottleneck) simulations remain. That is if $|L'| \leq |V| \times \epsilon_c$ the diffusion process in Algorithm~\ref{algo:diffusion-step} stops. Otherwise, $L$ is set to $L'$, $L'$ is cleared, and the next iteration starts. We used $\epsilon_c = 0.02$ to make \acro faster while keeping its quality almost the same.

Figure~\ref{fig:hyperdiff} shows a toy diffusion process on four vertices and a single sample. The process initializes sketches using respective hashes' number of leading zeros. Then larger numbers are started to be pulled from all recently changed neighbors. The same process is repeated for multiple vertices until the new seed vertex is found. To understand the benefits of estimating (instead of counting), we present Fig.~\ref{fig:infuserdiff} which shows an example in the same settings as Fig.~\ref{fig:hyperdiff}. One very important observation is that, in these examples, \acro{} computes the estimated influence for \emph{all} vertices with a single process, whereas {\sc InFuseR}, or another counting-based IM algorithm, only computes influence for a single vertex (vertex one in the example). Doing otherwise, i.e., computing the reachability set cardinalities for all the vertices at once for a given sample, may require $\mathcal{O}(n^2)$ memory and union operations with $\mathcal{O}(n)$ complexity. Although using CELF~\cite{CELF} optimization partially eliminates this problem by focusing only a few vertices, $\mathcal{O}(n)$ union complexity still remains.
%This is why although the reachability sets in Fig.~\ref{fig:infuserdiff} are shown for all vertices with dense vectors, the ones except that of vertex 1 are greyed out since they are not manipulated.
\begin{figure}[!ht]
    \begin{center}
    \includegraphics[width=0.95\linewidth]{images/sketchdiff.pdf}
    \caption{\acro diffusion process illustrated for \emph{all} vertices on toy sample graph. (a)\label{hyperinit} Toy sketch initialization. (b) \label{hyperdiff1} First level of diffusion using \emph{Pull-based} method for \emph{all} vertices. (c) \label{hyperdiff2} Second level diffusion following (a); only updated vertices' sketches are pulled. 
     }\label{fig:hyperdiff} 
    \end{center}
\end{figure}
\begin{figure}[!ht]
    \begin{center}
    \includegraphics[width=0.85\linewidth]{images/infuserdiff.pdf}
    \caption{{\sc InFuseR} diffusion process illustrated for \emph{only vertex $1$} on toy sample graph.  (a) \label{fig:infuserinit} Toy graph InFuseR initialization.  (b) \label{infuserdiff1} First level of diffusion using \emph{push-based} method for vertex $1$. (c) Second level of diffusion following Fig.\ref{fig:infuserdiff}(a).
     }\label{fig:infuserdiff} 
    \end{center}
\end{figure}

@@

\hline
\multirow{6}{*}{\scriptsize\rotatebox[origin=c]{90}{Directed}}&{\tt Epinions} & 75,880 & 508,838  & 6.71 & 14\\
&{\tt Friendster} & 65,608,366 & 1,806,067,135  & 27.53 & 32\\
&{\tt LiveJournal} & 4,847,571 & 68,993,773  & 14.23 & 16\\
&{\tt Pokec} & 1,632,803 & 30,622,564  & 18.75 & 11\\
&{\tt Slashdot0811} & 77,360 & 905,468  & 11.70 & 10\\
&{\tt Slashdot0902} & 82,168 & 948,464  & 11.54 & 11\\
% &{\tt Twitter} & 81,306 & 2,420,766 & 1.37 & 29.77 
\end{tabular}
}
\end{table}
% \FloatBarrier
\subsection{Experimental Settings} \label{sec:expset}

@@

We evaluated our method against four other state-of-the-art influence maximization algorithms, {\sc Tim+}, {\sc Skim}, {\sc Ripples}, and {\sc Ssa}. The first algorithm focuses on the influence score, whereas the second is a sketch-based algorithm that takes the execution time into account. The third one is a scalable, parallel approximation algorithm with a parameter to control the influence quality, and the last one leverages a Stop-and-Stare strategy.

@@

\item Minutoli et al.'s {\sc Ripples} is a high-performance, parallel algorithm that efficiently produces accurate seed sets~\cite{minutoli2019fast}. 
It is an approximation method that improves the Reverse Influence Sampling~(RIS)~\cite{borgs2014maximizing} algorithm by eliminating the need for the threshold to be used. %{\sc Ripples} generalizes the influence of all vertices on a small set of sample graphs that is sampled from the reachability sets of a few vertices. 
We have used $\epsilon = 0.5$ as suggested in the original paper, where $\epsilon$ is a user-defined parameter to control the approximation boundaries.

@@

\subsection{Comparing \acro with State-of-the-Art}
To compare the run time, memory use, and quality of \acro with those of the state-of-the-art, %As explained above, the parameters of the experimented methods are hard to compare directly. It is infeasible to find precisely the corresponding parameter between any two methods in this setting. For that reason, we have used the parameters suggested by the paper.
we perform experiments using the following parameters controlling the quality of the seed sets: {\sc Tim+} ($\epsilon=0.2$), {\sc Ripples} ($\epsilon=0.5$), {\sc Skim} ($l=64,k=64$), and {\sc Ssa}($\epsilon=0.1$). 
In fact, one of the drawbacks of \acro is that it does not have a direct control over the approximation factor, whereas {\sc Tim+} and {\sc Ripples} have one. Still, \acro can control the quality indirectly by tuning the number of Monte-Carlo simulations ${\cal J}$ which also increases the number of sketches used per vertex. In the experiments, we have used ${\cal J} = 256$ for \acro. In addition, as explained in the previous section, we use a global error threshold $\epsilon_{g} = 0.01$, a local error threshold as $\epsilon_l=0.3$, and the early-exit ratio as $\epsilon_{c}=0.02$.\looseness=-1
